This PDF is a Git Repository\\Containing its Own \LaTeX\ Source\\and a Copy of Itself

### 2017-05-05 article.tex
The Temple deserves capitals, no?
Added an in-joke
Added a license.

\begin{center}
\begin{tikzpicture}
\node at (0,0) (text) {\begin{minipage}{0.8\hsize}\small
As a matter of fact, G-d just questioned my judgement. He said,
`Terry, are you worthy to be the man who makes the temple? If you are,
you must answer: Is this [dastardly], or is this divine intellect?'
\end{minipage}};
\node[anchor=north east] at (text.north west) {\LARGE``};
\node[anchor=south west] at (text.south east) {\LARGE''};
\node[anchor=north east] at (text.south east) (terry) {\setbox9=\hbox{\llap{---}Terry A.\ Davis, creator of TempleOS}\parbox{\wd9}{\raggedright\box9 self-proclaimed ``smartest programmer that's ever lived''}};
\end{tikzpicture}
\end{center}

@@

>>>>

\begin{center}
\begin{tikzpicture}
\node at (0,0) (text) {\begin{minipage}{0.8\hsize}\small
As a matter of fact, G-d just questioned my judgement. He said,
`Terry, are you worthy to be the man who makes The Temple? If you are,
you must answer: Is this [dastardly], or is this divine intellect?'
\end{minipage}};
\node[anchor=north east] at (text.north west) {\LARGE``};
\node[anchor=south west] at (text.south east) {\LARGE''};
\node[anchor=north east] at (text.south east) (terry) {\setbox9=\hbox{\llap{---}Terry A.\ Davis, creator of TempleOS}\parbox{\wd9}{\raggedright\box9 self-proclaimed ``smartest programmer that's ever lived''}};
\end{tikzpicture}
\end{center}

Terry's not the only one who's written a compiler!

@@

\section{License}

Copyright \textcopyright\ 2017 Evan A.~Sultanik

Permission is hereby granted, free of charge, to any person obtaining a copy
of this document and associated source files (the ``Software''), to deal
in the Software without restriction, including without limitation the rights
to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
copies of the Software, and to permit persons to whom the Software is
furnished to do so, subject to the following conditions:

The above copyright notice, this permission notice, and the entire
contents and history of its associated git repository shall be
included in all copies or substantial portions of the Software.

\textsc{The Software is provided ``as is'', without warranty of any kind, express or implied, including but not limited to the warranties of merchantability, fitness for a particular purpose and noninfringement. In no event shall the authors or copyright holders be liable for any claim, damages or liability, whether in an action of contract, tort or otherwise, arising from, out of or in connection with the Software or the use or other dealings in the software.}
